Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Edit equation syntax

\section{Trading Model}

>>>>

\section{Trading Model}
In the following, we describe the data trading process in detail. To participate a data marketplace, data providers and consumers have to register first. Then data provider can launch its product on the marketplace. Once a product is launched, it is searchable and could be traded afterward. The whole trading and refunding process is defined in smart contracts which are easily traceable and irreversible.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys. Then some preselected brokers who are trustworthy are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.

Brokers certify session keys as well. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key to the broker. The broker signs the message and returns the signature to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.

The contract address and product description will be stored in a file which is uploaded to IPFS. Consumers can search the desired product by keywords or tags. The consumer then evaluates the product and start trading with the data provider if the consumer is interested in subscribing the data.

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and subscribers. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber. After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts. For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract. Subscribers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Subscribers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and subscribers can download and decrypt them with the session¸

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the subscribers pay the subscription fee. To protect subscribers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, subscribers can ask for refunds. We assume that less than half of subscribers in the Product Contract are irrational and malicious. Each subscriber can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber. The subscription fee can be prorated as below:

\begin{equation}
F_{DataProvider}(k) = N price \frac{k-1}{M} (1-F_{b}) (1-F_{t})
\end{equation}

\begin{equation}
F_{Broker}(k) = N price \frac{k-1}{M} F_{b} (1-F_{t})
\end{equation}

\begin{equation}
F_{Consumer}(k) = price \frac{M-k+1}{M} (1-F_{t})
\end{equation}

Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.
